Think deep for reef resilience

### 2025-08-10 paper/paper_draft.qmd
Add note for @eco-ben

## Depth estimation

Reef depth characteristics were extracted using 10m resolution bathymetry data from the
Great Barrier Reef Marine Park Authority (GBRMPA [-@GBRMPA2020]). For each reef, bathymetry
data (in raster format) were spatially matched with reef polygon features through geometric
intersection analysis. Depth values within each reef polygon were summarized using zonal
statistics to calculate minimum, mean, median, maximum, and standard deviation of depth
values. All depth values were converted to positive values (depths below sea level). The
median depth was used to provide an indicative depth value for each reef.

>>>>

**\[TI: Ben, best to use the same colours consistently for each management region. Blue,
yellow/orange, green and pink were used in for the map.\]**
Reef depth characteristics were extracted using 10m resolution bathymetry data from the
Great Barrier Reef Marine Park Authority (GBRMPA [-@GBRMPA2020]). For each reef, bathymetry
data (in raster format) were spatially matched with reef polygon features through geometric
intersection analysis. Depth values within each reef polygon were summarized using zonal
statistics to calculate minimum, mean, median, maximum, and standard deviation of depth
values. All depth values were converted to positive values (depths below sea level). The
median depth was used to provide an indicative depth value for each reef.
